---
title: "`r params$title`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: tango
params:
  title: "ClinicalBayes Analysis Report"
  # Binary Arm
  priors: NULL
  ctrl_post: NULL
  decision: NULL
  oc: NULL
  comm: NULL
  # Continuous Arm
  cont_ctrl: NULL
  cont_decision: NULL
  cont_oc: NULL
  comm_cont: NULL
---

```{r setup, include=FALSE}
# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE, 
  fig.width = 10, 
  fig.height = 6
)

# Null coalescing operator
`%||%` <- function(x, y) if (is.null(x)) y else x

# Libraries
library(ggplot2)
library(DT)
library(dplyr)
library(rstan)
library(bayesplot)
library(scales)
library(htmltools)

# For Stan plots in RMarkdown
options(device = function(...) {
  pdf(file = NULL)
  dev.control("enable")
})
```

# 1. Executive Summary

This report provides a formal summary of the Bayesian clinical trial analysis. It documents the prior distributions elicited from historical data, the resulting posterior distributions, and the formal decision metrics regarding treatment efficacy.

# 2. Binary Endpoint Analysis

```{r, results='asis', ev}
if (is.null(params$decision)) {
  cat("\n> **Status:** No binary analysis data found in this session.\n")
} else {
  cat("### Posterior Decision Metrics\n\n")
  cat("**Pr(Treatment Effect > Δ* | Data):** ", 
      round(params$decision$prob %||% 0, 4), "\n\n")
  
  if (!is.null(params$ctrl_post)) {
    cat("### Control Arm Prior & Posterior\n")
    # This assumes ctrl_post is a ggplot object or has a plot method
    print(params$ctrl_post)
  }
}
```

## Binary Operating Characteristics

```{r, results='asis'}
if (is.null(params$oc)) {
  cat("_Operating characteristics not simulated for binary endpoints._\n")
} else {
  cat("The following analysis demonstrates the frequentist power and Type-I error across a grid of true response rates.\n")
  # If params$oc is the result of the simulation, plot the power curve
  print(params$oc$plot %||% params$oc) 
}
```

# 3. Continuous Endpoint Analysis

```{r, results='asis'}
if (is.null(params$cont_decision)) {
  cat("\n> **Status:** No continuous analysis data found in this session.\n")
} else {
  cat("### Posterior Decision Metrics\n\n")
  cat("**Pr(μ_t - μ_c > Δ* | Data):** ", 
      round(params$cont_decision$prob %||% 0, 4), "\n\n")
  
  if (!is.null(params$cont_ctrl)) {
    cat("### Continuous Control Posterior Summary\n")
    if(is.data.frame(params$cont_ctrl)) {
      # Use tagList to ensure HTML widget renders inside asis chunk
      cat(as.character(tagList(datatable(params$cont_ctrl, options = list(dom = 't')))))
    } else {
      print(params$cont_ctrl)
    }
  }
}
```

## Continuous Operating Characteristics

```{r, results='asis'}
if (is.null(params$cont_oc)) {
  cat("_Operating characteristics not simulated for continuous endpoints._\n")
} else {
  cat("Simulation results for continuous endpoints.\n")
  print(params$cont_oc$plot %||% params$cont_oc)
}
```

# 4. Commensurate Borrowing Models (Stan)

Dynamic borrowing utilizes the Commensurate Prior model to weigh historical evidence based on its consistency with the current trial data.

## Model Diagnostics & Borrowing Strength

```{r, results='asis'}
if (is.null(params$comm) && is.null(params$comm_cont)) {
    cat("*No commensurate models (Stan) were fitted in this session.*\n")
} else {
    cat("The posterior distribution of the commensurability parameter (τ) indicates the weight assigned to historical data.\n")
    
    if (!is.null(params$comm)) {
        cat("#### MCMC Trace Plots (Binary Commensurate)\n")
        print(mcmc_trace(as.array(params$comm), pars = "tau"))
    }
    
    if (!is.null(params$comm_cont)) {
        cat("#### MCMC Trace Plots (Continuous Commensurate)\n")
        print(mcmc_trace(as.array(params$comm_cont), pars = "tau"))
    }
}
```

# 5. Technical Metadata

- **Generator:** ClinicalBayes v1.0  
- **Analysis Engine:** Stan (MCMC) & Analytical Conjugate Priors  
- **Rendered At:** `r Sys.time()`  
- **R Version:** `r R.version.string`

<div style="margin-top: 50px; text-align: center; border-top: 1px solid #eee; padding-top: 20px; color: #777;">
Analysis Report
</div>
